---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ea

<!-- badges: start -->
[![R-CMD-check](https://github.com/simonmoulds/ea/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/simonmoulds/ea/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The ea package provides access to Environment Agency (EA) Hydrology API.

## Installation

You can install the development version of ea from [GitHub](https://github.com/) with:

```{r message=FALSE}
devtools::install_github("simonmoulds/ea")
```

## Example

Here is a basic example that shows you how to use the package to download streamflow timeseries data from the EA Hydrology API:

```{r message=FALSE}
library(dplyr)
library(lubridate)
library(ggplot2)
library(ea)
```

First we get discharge stations on the River Thames within 5km of Abingdon:
```{r}
stns <- ea_station_list(
  sample_of = "River Thames", observed_property = "waterFlow",
  lat = 51.6708, long = -1.2880, dist = 5
)
stns
```

There is only one station available. We extract its global unique identifier (GUID), and use `ea_timeseries_list` to retrieve the available timeseries data:
```{r}
guid <- stns$stationGuid
tslist <- ea_timeseries_list(guid)
tslist
```

We can see that there are several timeseries available for this station, each referenced with a unique measurement ID provided in the `notation` column. We retrieve the ID for daily mean flow:
```{r}
measure <- tslist |>
  filter(period == 86400 & valueType == "mean") |> 
  pull(notation)
measure
```

We can use the measurement ID to retrieve the timeseries data:
```{r}
min_date <- Sys.Date() %m-% months(3)
ts <- ea_timeseries_values(measure, min_date = min_date)
ts
``` 

Alternatively, we can supply the station GUID and some additional parameters to retrieve the timeseries data:
```{r}
ts <- ea_timeseries_values(
  station_guid = guid, observed_property = "waterFlow",
  value_type = "mean", period = 86400, min_date = min_date
)
ts
```

Once we have obtained the data we can plot the timeseries:

```{r, echo = FALSE}
p <- ggplot(data = ts, aes(x = date, y = value)) + geom_line() + xlab("") + ylab(expression(paste("Daily mean flow [", m^3, "/", s, "]"))) + theme_bw()
p
```

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
