---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ea

<!-- badges: start -->
[![R-CMD-check](https://github.com/simonmoulds/ea/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/simonmoulds/ea/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The ea package provides access to Environment Agency (EA) Hydrology API.

## Installation

You can install the development version of ea from [GitHub](https://github.com/) with:

```{r}
devtools::install_github("simonmoulds/ea")
```

## Example

Here is a basic example that shows you how to use the package to download streamflow timeseries data from the EA Hydrology API:

```{r example}
library(dplyr)
library(lubridate)
library(ggplot2)
library(ea)
```

The steps required to download historical streamflow data are outlined below: 
```{r}
# Get discharge stations on the River Thames within 5km of Abingdon
abingdon_stations <- ea_station_list(
  sample_of = "River Thames", observed_property = "waterFlow",
  lat = 51.6708, long = -1.2880, dist = 5
)
guid <- abingdon_stations$stationGuid
tslist <- ea_timeseries_list(guid)

# Filter to get daily mean flow 
measure <- tslist |>
  filter(period == 86400 & valueType == "mean") |> 
  pull(notation)
min_date <- Sys.Date() %m-% months(3)
ts <- ea_timeseries_values(measure, min_date = min_date)

# Alternatively: 
ts <- ea_timeseries_values(
  station_guid = guid, observed_property = "waterFlow",
  value_type = "mean", period = 86400, min_date = min_date
)
```

Once we have obtained the data we can plot the timeseries:

```{r, echo = FALSE}
p <- ggplot(data = ts, aes(x = date, y = value)) + geom_line()
p
```

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
